Re-finding to support a Deep Web Question Answering System

### 2010-03-04 trunk/paper/semsearch10/content/ontological_realms.tex
fourth round of changes by jnw

\subsection{Category Heterarchy} 
% Author: Clint 
Since, our representation of semi structured query [citation needed]
is in OWL ontology format, and our aim is to compare and rank the
queries in this format, we had to define a similarity measure between
ontologies. The defined ontology class comparison measure "class
divergence" [citation needed] assumes that we have an ontology store
with unambiguous interpretation of classes and strict hierarchical
subclass super class relationships and the classes to be compared
should belong to it. We cannot find any robust existing ontology
library of that nature for this purpose. So we decided to build a new
ontology store and as an initial step the categories from DBPedia
store [citation needed] are used. Even though, some of these
categories are loosely coupled and not fully agreed upon the sub
category and super category relationships, this DBPedia has enormous
amount of data in linked form [citation needed]. The OWL ontology
[citation needed] format is followed in this process. The DBPedia
categories are converted into OWL ontology classes and the super class
- sub class relationships are built using the OWL super class sub
class axioms [citation needed]. Another reason for selecting OWL for
this purpose is that we can make use of the existing APIs for building
and reasoning [citation needed] the ontology relationships.

@@

\subsection{Associating Terms with Categories} %joir-dan The
subcategories of the category Automobiles (… Driving, Traffic Law,
Automobiles by Decade, Auto Racing…) can be seen as grabbing
information specific to the category. The supercategories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motorsport, Individual Sport...) are an abstract description of
the subcategories.

>>>>

\section{Representing and Ontological Realms}
\subsection{Category Heterarchy} 
% Author: Clint 
Two types of ontologies are used by our system:
\begin{enumerate}
\item Realm ontologies, comprising a heterarchy of categories that
  characterize terms that can appear in queries.
\item SSQ ontologies, used to describe the form of particular
  realm-specific queries.
\end{enumerate}
For any particular ontological realm, the number of potential
terms and their associated categories can be quite large.
Construction of a realm ontology and the terms associated
with its categories would be an extremely laborious task
for any non-trivial realm. The realm of automobiles (which
we use for illustration in this paper) contains, for example,
over XXXX categories and XXXX terms. We were unable to find
an appropriate ontology for this realm, so we constructed it
using categories from the DBPedia [!!!! citation needed].
The primary benefit of using the DBPedia for this purpose is
that not only does it supply a categorical heterarchy, but it
also links to wikipedia documents which provides us with a large
realm-specific document corpus.

To support our process, we map DBPedia categories into classes in our
realm ontology with the superclass/subclass relationships built using
DBPedia properties broader/narrower.  By using OWL, we can exploit the
OWL API for matching SSQ ontologies that reference these realm
ontologies.

@@

\subsection{Associating Terms with Categories}
%joir-dan

Once the semantic hierarchy is created, the next step is to create
training data for the system. The task is then to grab the pages,
build a corpus relating to a given category, and then compile the
information in a meaningful way. The overall goal is to grab enough
information to properly characterize a category while limiting the
amount of unnecessary content within the corpus. The problem with this
approach is the page density varies greatly across the
heterarchy. Each category within the DBpedia/ Wikipedia heterarchy
contains a set of information pages, P, that correspond to concepts
that share said category. Considering that the categorical structure
is a directed acyclic graph \cite{Suchanek07yago:a}, we consider the
use of a Markov Blanket \cite{Friedman97bayesiannetwork} in describing
a particular category. The category's that The assumption is that a
node can be fully described by its ancestor, descendant, and spousal
nodes (parent node of subcategory not equal to the category). While
this does not completely solve the issue of a category residing in a
sparse area of the graph, the amount of information that can be
obtained per blanket is usually more helpful than per category.

The subcategories of the category Automobiles (… Driving, Traffic Law,
Automobiles by Decade, Auto Racing…) can be seen as grabbing
information specific to the category. The supercategories (Road
Vehicles) place the category in a higher perspective, abstractly
describing basketball as a concept. The spousal categories
(...Motorsport, Individual Sport...) are an abstract description of
the subcategories.
